---
title: "CV - Tamas Szilagyi"
output: html_document
---

email: tszilagyi@outlook.com /
mobile: +31 61 887 9150 /
[LinkedIn](https://www.linkedin.com/in/tszilagyi) /
[StackOverflow](http://stackoverflow.com/users/4964651/mtoto?tab=profile) 

## Work


```{r, echo = FALSE}
source("data.R")
```

#### Timeline Work Experience
```{r,results='asis', echo = F, out.height = 100, cache =FALSE}
suppressPackageStartupMessages(library(googleVis))

# Timeline chart example
op <- options(gvis.plot.tag='chart')
timel<-gvisTimeline(cv1, barlabel="Position", rowlabel="Group",
                  start="StartDate", end="EndDate",
                  options=list(
                    timeline="{barLabelStyle:{fontSize:9},
                    showBarLabels: true}", width = 900))
plot(timel)
```

#### Digital Analyst at Transavia
*Data Layer Development, Data Processing, Experimentation, Predictive Modeling.*  
Built first data product for transavia.com in form of a destination recommender engine.

#### Campaign Analytics at Achtung!
*KPI-centric IO-design, Tagging, Dashboarding, AB-testing, Optimization, Campaign Evaluation.*  
Lead more than 25 analytics projects for A-list clients on all digital platforms imaginable.

#### Planner at Tribal DDB
*Social Media Analytics, Content Strategy, Social Advertising Performance Optimization.*  
Presented content analytics findings underpinning yearly Social Strategy Plan for Heineken.

#### Nabit Evangelist at CloudRaker
*App Analytics, UX Optimization, Growth Hacking, Organic Media Strategy and PR.*  
Lead organic media strategy and optimization of in-house app, reaching 2 million downloads.

### Relevant Skills in Most Recent Jobs
```{r,results='asis', echo = F}
Column1 <- gvisColumnChart(s1, options = 
                            list(vAxes="[{viewWindowMode:'explicit',
                                 viewWindow:{min:0, max:10},title:'Skills'}]",
                                 colors="['#34A853']",
                                 legend = "none",
                                 title = "Web Analytics Tools",
                                 width = 225, height = 225))

Column2 <- gvisColumnChart(s2, options = 
                            list(vAxes="[{viewWindowMode:'explicit',
                                 viewWindow:{min:0, max:10},title:'Skills'}]",
                                 colors="['#EA4335']",
                                 legend = "none",
                                 title = "Online Advertising Tools",
                                 width = 225, height = 225))

Column3 <- gvisColumnChart(s3, options = 
                            list(vAxes="[{viewWindowMode:'explicit',
                                 viewWindow:{min:0, max:10},title:'Skills'}]",
                                 colors="['#EEB211']",
                                 legend = "none",
                                 title = "Data Science Tools",
                                 width = 225, height = 225))

Column4 <- gvisColumnChart(s4, options = 
                            list(vAxes="[{viewWindowMode:'explicit',
                                 viewWindow:{min:0, max:10},title:'Skills'}]",
                                 colors="['#4285F4']",
                                 legend = "none",
                                 title = "Coding Tools",
                                 width = 225, height = 225))

colors = "['#4285F4', '#34A853', '#D50F25','#EEB211', '#FBBC05', '#DB4437', '#EA4335']"

opts <- paste0("{
        link: { colorMode: 'gradient',
               colors: ", colors ," },
               node: { colors: ", colors ," },
               iteration: 0
               }" )

Sankey <- gvisSankey(jobsSK, from="From", to="To", weight="Weight",
                     options=list(
                       sankey=opts,
                       width = 450, 
                       heigth = 450))

obj1<-gvisMerge(Column1, Column2, horizontal = TRUE)
obj2<-gvisMerge(Column3, Column4, horizontal = TRUE)
obj3<-gvisMerge(obj1, obj2, horizontal = FALSE)
obj4<-gvisMerge(Sankey,obj3, horizontal = TRUE)

plot(obj4)
```

## Studies


#### Timeline Studies
```{r,results='asis', echo = F}
# Timeline chart example
time1<-gvisTimeline(cv2, barlabel="Position", rowlabel="Group",
                  start="StartDate", end="EndDate",
                  options=list(
                    timeline="{barLabelStyle:{fontSize:9},
                    showBarLabels: true}", width = 900))
plot(time1)
```


#### Bsc. in Communication Sciences at KU Leuven
*Statistics I & II, Behavioral Research Methods, Philosophy, Anthropology of Art and Popular Culture.*

#### Exhange Semester at the University of Jönköping
*Business Statistics, Marketing Management, Research Methods: Design, Implementation and Analysis.*  

#### MLitt. in Management at University of St Andrews
*Business Research Methods, Strategic Management in the Information Age, Alternative Investments.*  
Thesis: The Sustainability of the US Dollar as an Internatinal Reserve Currency.

<br>

## Languages, Interests and Accomplishments

### Accomplishments

- Best Newbie Session at [MeasureCamp London 2015]("http://www.measurecamp.org/"): *'How Transavia uses Decision Trees to Cross- and Up-Sell'*.
- 4-times Hungarian Champion in Sabre Fencing in team, 2nd place individually in 2001 .

### Interests
- Trekked accross Knoydart in the Highlands, the last wilderness of the UK.
- Supported causes include kiva.org, and Hungarian Transparency NGO atlatszo.hu.

### Languages
```{r fig.width=3, fig.height=1,echo=FALSE}
library(png)
library(grid)
img <- readPNG("img/flags.png")
grid.raster(img)
```

```{r}
# CV is built using rmakrdown in combination with googleVis. Source code: https://github.com/mtoto/CV
```